---
title: "p8105_hw1_xx2416"
author: "Xicheng Xie"
output: github_document
date: "2022-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Solution 1

This is the solution to the **problem 1**
```{r Problem 1}
install.packages("palmerpenguins",repos = "http://cran.us.r-project.org")
library("tidyverse")
data("penguins",package = "palmerpenguins")
force(penguins)
```

Here I am going to create an overall summary table for **penguins**
```{r}
library("gtsummary")
penguins%>%
  tbl_summary(missing_text = "Missing",
              statistic = list(all_continuous()~"{mean} ({sd})"),
              
              label = list(species ~ "Species",
                           island ~ "Island",
                           sex ~ "Sex",
                           year ~ "Year"))%>%
  bold_labels()%>%
  italicize_levels()
```
This is a very beautiful table, but we still need to do some discussion.
The names and classes of each variables in **penguins** are `r names(penguins)` and `r str(penguins)`. The size of **penguins** is `r nrow(penguins)`x`r ncol(penguins)`. The mean flipper length can be easily calulated, which is `r mean(pull(penguins, flipper_length_mm))`

### embed a scatterplot
Here is a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
```{r scatterplot}
ggplot(penguins, aes(bill_length_mm, flipper_length_mm, colour=species))+
  geom_point()
ggsave("scatterplot.png")
  
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
