---
title: "p8105_hw1_xx2416"
author: "Xicheng Xie"
output: github_document
date: "2022-09-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Solution of problem 1

This is the solution to the **problem 1**
```{r Problem 1, eval=FALSE}
install.packages("palmerpenguins",repos = "http://cran.us.r-project.org")
```

Here I am going to create an overall summary table for **penguins**
```{r,warning=FALSE}
data("penguins",package = "palmerpenguins")
force(penguins)
library("gtsummary")
library("tidyverse")
penguins%>%
  tbl_summary(missing_text = "Missing",
              statistic = list(all_continuous()~"{mean} ({sd})"),
              
              label = list(species ~ "Species",
                           island ~ "Island",
                           sex ~ "Sex",
                           year ~ "Year"))%>%
  bold_labels()%>%
  italicize_levels()
mean(penguins$flipper_length_mm)
```
This is a very beautiful table, but we still need to do some discussion.
The names and classes of each variables in **penguins** are `r names(penguins)` and `r str(penguins)`. The size of **penguins** is `r nrow(penguins)`x`r ncol(penguins)`. The mean flipper length can be easily calulated, which is `r mean(pull(penguins, flipper_length_mm),na.rm=TRUE)`.

### embed a scatterplot
Here is a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
```{r scatterplot, warning=FALSE}
ggplot(penguins, aes(bill_length_mm, flipper_length_mm, colour=species))+
  geom_point()
ggsave("scatterplot.png")
```

# Solution of problem 2

Create a data frame comprised of:

a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”
```{r create df}
p2_df<-tibble(
  norm_sample=rnorm(10,mean = 1),
  norm_sample_pos= norm_sample>0,
  chr=c("a","b","c","d","e","f","g","h","i","j"),
  fr=factor(case_when(norm_sample>0~"large",
               norm_sample>=0 & norm_sample<1~"medium",
               norm_sample<0~"small"))
)

```
Then we try to take the mean of eahc variable in **p2_df**
* The mean of **norm_sample** is `r mean(pull(p2_df,norm_sample))`
* The mean of **norm_sample_pos** is `r mean(pull(p2_df,norm_sample_pos))`
* The mean of **chr** is `r mean(pull(p2_df,chr))`
* The mean of **fr** is `r mean(pull(p2_df, fr))`

### Variable type convertion
```{r ,eval=FALSE}
as.numeric(pull(p2_df,norm_sample_pos))
as.numeric(pull(p2_df,chr))
as.numeric(pull(p2_df,fr))
```

When convert **norm_sample_pos** to numeric variable, TRUE and FALSE are converted 1 and 0, so its mean can be calculated. For character and factor variables, their means cannot be calculated. 
As we can see in the results, **chr** and **fr** are not numeric or logical and NA is returned when calculating their means. **chr** is a character, as.numeric will return NA; **fr** is a factor, as.numeric will return the underlying numeric representation of each level.
